Dynamic Prediction of Non-Guassian Outcome with fast Generalized Functional Principal Analysis

### 2023-03-14 Write-ups/Manuscript.Rmd
calculated AUC and ISE of fGFPCA

# other quantities
mid <- unique(exp_df$bin)
N <- 500
M <- length(pred_lst)
J <- 1000

@@

  # calculate AUC
  auc_mt <- rep(NA, 4) 
  for(t in c(200, 400, 600, 800)){

    # predicted value
    pred_name <- paste("pred_t", t, sep = "")
    pred_mat <- pred_lst[[m]] %>% select(id, bin, all_of(pred_name)) %>% 
      pivot_wider(names_from = id, values_from = pred_name) %>%
      column_to_rownames("bin")
    pred_full <- sapply(1:N,
                           function(x){approx(x=mid, y=pred_mat[ , x], xout = 1:J)$y})
    pred_full <- exp(pred200_full)/(1+exp(pred200_full))
    row_id <- complete.cases(pred_full)
    auc_perf <- performance(prediction(pred_full[row_id, ], Y_mat[row_id, ]), "auc")
    auc_mt[t] <- mean(unlist(auc_perf@y.values))
  }

  pred_eta <- pred_lst[[m]] %>% select(-eta_hat)
  pred_eta <- pred_eta %>% left_join(true_eta, by = c("id", "bin"))
}
```

>>>>

# other quantities
mid <- unique(pred_lst[[1]]$bin)
N <- 500
M <- length(pred_lst)
J <- 1000

@@

  # calculate AUC
  t_vec <- c(200, 400, 600, 800)
  for(i in seq_along(t_vec)){

    t <- t_vec[i]
    # predicted value
    pred_name <- paste("pred_t", t, sep = "")
    pred_mat <- pred_lst[[m]] %>% select(id, bin, all_of(pred_name)) %>% 
      pivot_wider(names_from = id, values_from = pred_name) %>%
      column_to_rownames("bin")
    pred_full <- sapply(1:N,
                           function(x){approx(x=mid, y=pred_mat[ , x], xout = 1:J)$y})
    pred_full <- exp(pred_full)/(1+exp(pred_full))
    row_id <- complete.cases(pred_full)
    auc_perf <- performance(prediction(pred_full[row_id, ], Y_mat[row_id, ]), "auc")
    auc_mat[m, i] <- mean(unlist(auc_perf@y.values))
  }

}

auc_mat
```

### 2023-03-14 Write-ups/Manuscript.tex
calculated AUC and ISE of fGFPCA

>>>>

\begin{verbatim}
## Warning: Using an external vector in selections was deprecated in tidyselect 1.1.0.
## i Please use `all_of()` or `any_of()` instead.
##   # Was:
##   data %>% select(pred_name)
## 
##   # Now:
##   data %>% select(all_of(pred_name))
## 
## See <https://tidyselect.r-lib.org/reference/faq-external-vector.html>.
\end{verbatim}

\begin{verbatim}
##           t200      t400      t600      t800
## [1,] 0.6831917 0.7072828 0.6962669 0.6216755
## [2,] 0.6881236 0.7011135 0.6886562 0.6203330
## [3,] 0.6903756 0.7055576 0.6949729 0.6219840
## [4,] 0.6869610 0.6983328 0.6946955 0.6178570
## [5,] 0.6857926 0.7086377 0.6983496 0.6223322
\end{verbatim}
